Shorten Amicus Text

### 2022-01-26 data-cleaning/01-shorten-amicus-text.Rmd
identified ids where no text removed close #1

@@

There are only 52 briefs remaining that mention an appendix that have not already had their appendix removed.

>>>>

```{r}
#saving these ids to a csv
footnotes_not_removed <- a %>% filter(footnotes > 0) %>% select(id)

#box_write(footnotes_not_removed,
#          file_name = "footnotes-not-removed.csv",
#          dir_id = 145990409196)
```

@@

There are only 62 briefs remaining that mention an appendix that have not already had their appendix removed.

```{r}
#saving these ids to a csv
appendix_not_removed <- a %>% filter(appendix_all > 0) %>% select(id)

#box_write(appendix_not_removed,
#          file_name = "appendix-not-removed.csv",
#          dir_id = 145990409196)
```
